A unified model for parsing and sentence understanding

### 2016-03-14 writing/hard_stack_paper/paper.tex
Improve runtime results report
axis labels

\begin{figure}
\begin{tikzpicture}
\begin{axis}[xlabel=Batch size, ylabel=Feedforward time (sec),
			 legend style={anchor=north west}]
  \addplot table [x={Batch size}, y=CPU, col sep=tab] {runtime.csv};
  \addlegendentry{CPU}
  \addplot table [x={Batch size}, y=GPU, col sep=tab] {runtime.csv};
  \addlegendentry{Thin-stack GPU}
\end{axis}
\end{tikzpicture}
\caption{Runtime performance results with the thin-stack GPU algorithm for tree-structured neural networks. \todo{[JG] Add some comments, avg points, add larger batch sizes for thin-stack}}
\end{figure}

>>>>

\begin{figure}
\resizebox{\linewidth}{!}{
\begin{tikzpicture}
\begin{axis}[xmin=0, ymin=0, xlabel=Batch size, ylabel=Feedforward time (sec),
			 xtick={0,256,512,1024,2048}, legend style={at={(1, 1)},anchor=north east}]
  \addplot table [x={Batch size}, y=CPU, col sep=tab] {runtime.csv};
  \addlegendentry{CPU \cite{irsoy2014deep}}
  \addplot table [x={Batch size}, y=GPU, col sep=tab] {runtime.csv};
  \addlegendentry{Thin-stack GPU}
\end{axis}
\end{tikzpicture}
}
\caption{Runtime performance results with the thin-stack GPU algorithm for tree-structured neural networks. \todo{[JG] Add some comments}}
\end{figure}
